Incentivizing Exploration with Unbiased History

### 2018-11-02 llevel-overview.tex
editing...

 \draw [rounded corners=3mm, line width=1mm, red](-0.2,4.8)--(2.2,4.8)--(2.2,6.2)--(-0.2,6.2)--cycle;
  \draw [rounded corners=3mm, line width=1mm, red](5.8,4.8)--(8.2,4.8)--(8.2,6.2)--(5.8,6.2)--cycle;
\end{tikzpicture}
\caption{Connecting structures between levels for the $L$-level policy.}
\label{fig:llevel-connecting}
\end{figure}

@@

In the $L$-level policy, such boundary case occurs for each
intermediate level $l\in \{2, \ldots, l-1\}$, but issue mentioned
above does not get naturally resolved as in some of these boundary
cases---the ratios between the upper and lower bounds of $\Delta$ rise
from $\Theta(\sqrt{\log(T)})$ to $\Theta(\log(T))$, and it would
require more observations from level $(l-2)$ to distinguish two arms
at level $l$. The reason for this larger disparity is that, except the
first level, we can no longer guarantee sufficient number of pulls of
each arm. For example, as shown in Figure \ref{fig:llevel-connecting},
when we talk about having enough arm $a$ pulls in the history observed
by agents in $G_{l,1,1}$, it could be that only agents in group
$G_{l-1,1,1}$ are pulling arm $a$ and it also could be that most
agents in groups $G_{l-1,1,1},G_{l-1,1,2},...,G_{l-1,1,\NG}$ are
pulling arm $a$. Therefore our estimate of the number of arm $a$ pulls
can be off by an $\NG=\Theta(\log(T))$ multiplicative factor. This
finally makes the boundary cases harder to deal with.

In our $L$-level policy, after understanding the boundary cases well, we resolve this problem by introducing an additional type of groups: $\Gamma$-groups. For each $l \in [L], u,v \in [\NG]$, we create a $\Gamma$-group $\Gamma_{l,u,v}$. Agents in $\Gamma_{l,u,v}$ observe the same history as the one observed by agents in $G_{l,u,v}$ and the number of agents in $\Gamma_{l,u,v}$ is $\Theta(\log(T)$ times the number of agents in $G_{l,u,v}$. The main difference between the $G$-groups and $\Gamma$-groups is that the history of $\Gamma$-groups in level $l$ is not sent to agents in level $l+1$ but agents in higher levels. When we are in the boundary case in which we don't have good guarantees about the $l+1$ level agents' pulls, the new construction makes sure that agents in levels higher than $l+1$ get enough pulls of each arm and all pull the best arm. 
%%% Local Variables:
%%% mode: latex
%%% TeX-master: "main"
%%% End:

>>>>

 \draw [rounded corners=3mm, line width=1mm, red](-0.2,4.8)--(2.2,4.8)--(2.2,6.2)--(-0.2,6.2)--cycle;
  \draw [rounded corners=3mm, line width=1mm, red](5.8,4.8)--(8.2,4.8)--(8.2,6.2)--(5.8,6.2)--cycle;
\end{tikzpicture}
\caption{Interlacing connections between levels for the $L$-level policy.}
\label{fig:llevel-connecting}
\end{figure}

@@

In the $L$-level policy, such boundary case occurs for each
intermediate level $l\in \{2, \ldots, l-1\}$, but issue mentioned
above does not get naturally resolved as in some of these boundary
cases---the ratios between the upper and lower bounds of $\Delta$ rise
from $\Theta(\sqrt{\log(T)})$ to $\Theta(\log(T))$, and it would
require more observations from level $(l-2)$ to distinguish two arms
at level $l$. The reason for this larger disparity is that, except the
first level, we can no longer guarantee sufficient number of pulls of
each arm. For example, as shown in Figure \ref{fig:llevel-connecting},
when we talk about having enough arm $a$ pulls in the history observed
by agents in $G_{l,1,1}$, it could be that only agents in group
$G_{l-1,1,1}$ are pulling arm $a$ and it also could be that most
agents in groups $G_{l-1,1,1},G_{l-1,1,2},...,G_{l-1,1,\NG}$ are
pulling arm $a$. Therefore our estimate of the number of arm $a$ pulls
can be off by an $\NG=\Theta(\log(T))$ multiplicative factor. This
ultimately makes the boundary cases harder to deal with.

We resolve this problem by introducing an additional type of \emph{amplifying groups}: $\Gamma$-groups. For each $l \in [L], u,v \in [\NG]$, we create a $\Gamma$-group $\Gamma_{l,u,v}$. Agents in $\Gamma_{l,u,v}$ observe the same history as the one observed by agents in $G_{l,u,v}$ and the number of agents in $\Gamma_{l,u,v}$ is $\Theta(\log(T)$ times the number of agents in $G_{l,u,v}$. The main difference between the $G$-groups and $\Gamma$-groups is that the history of $\Gamma$-groups in level $l$ is not sent to agents in level $l+1$ but agents in higher levels. When we are in the boundary case in which we don't have good guarantees about the $l+1$ level agents' pulls, the new construction makes sure that agents in levels higher than $l+1$ get enough pulls of each arm and all pull the best arm. 
%%% Local Variables:
%%% mode: latex
%%% TeX-master: "main"
%%% End:
